Linear variation and an optimization of algorithms for connected components labeling in a binary image

### 2016-02-06 paper/paper.tex
Add benchmark tables for several sizes
Return TwolineDsuCounter back, some polish
Some more polish for tables
Add overview for DFS and start one for SUF

>>>>

In this section we present performance benchmarks of some popular methods for
counting CC both with and without the $2 \times 2$ cells optimization.

\subsection{Algorithms overview}

\subsubsection{DFS}

The first algorithm we chose for the benchmark is Depth First Search graph traversal.
Graph traversal algorithms are the general approach for CC labeling in graphs, and
DFS is arguably the most simple.
Although not intended for image labeling and
suboptimal in most cases, it still has linear in the number of pixels worst-case
complexity in both time and memory.

Like most approaches, the algorithm contains has and outer loop over all pixels
of the image.
Each time an object pixel that is not labeled yet is encountered, DFS traversal
is launched from that pixel.
The traversal labels all the object pixels of the same CC, launching recursively
from all unlabeled neighbors of current pixel.

\subsubsection{SUF}

Another general approach for graph CC labeling which is more popular in image
labeling is using some kind of a data structure to maintain disjoint sets of pixels
that are considered to be in the same CC.
The structure is commonly called \texttt{Union-Find}, as the two essential operations
it must support are \texttt{Union}, which is used to union some of the disjoint sets,
and \texttt{Find}, which is used to find the representative element of the set
some element belongs to, so that we can always tell if two elements are in the same
set.

\subsubsection{SUF2}

\subsubsection{DTSUF}

\newcommand{\inputtable}[2]{
  \begin{table}[p]
    \centering
    \input{../bench-out/#1x#2}
    \caption{Noise images $#1 \times #2$ px}
    \label{tab:noise#1x#2}
  \end{table} }

% \inputtable{200}{300}
% \inputtable{400}{600}
\inputtable{800}{1200}
% \inputtable{1200}{1800}
\inputtable{2000}{3000}
\inputtable{4000}{6000}
